The \dealii{} Library, Version 9.0

### 2018-04-11 9.0/paper.tex

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

\author[8]{Jean-Paul Pelteret}
\affil[8]{Chair of Applied Mechanics,
  University of Erlangen-Nuremberg,
  Egerlandstr.\ 5,
  91058 Erlangen,
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}

\author[10]{David Wells}
\affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA.
  {\texttt{wellsd2@rpi.edu}}}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
\marginpar{update}
  Rajat Arora,
  Mauro Bardelloni,
  Conrad Clevenger,
  Sam Cox,
  Toby D. Young,
  Juliane Dannberg,
  Nicola Demo,
  Patrick Esser,
  Niklas Fehn,
  Rene Gassmoeller,
  Joscha Gedicke,
  Nicola Giuliani,
  Sebastian Gonzalez-Pintor,
  Ryan Grove,
  Michael Harmon,
  Daniel Jodlbauer,
  Guido Kanschat,
  Justin Kauffman,
  Eldar Khattatov ,
  Uwe Koecher,
  Alex Kokomov,
  Paul Kuberry,
  Dustin Kumor,
  Konstantin Ladutenko,
  Karl Ljungkvist,
  Andrew McBride,
  Mathias Mentler,
  Andrea Mola,
  Dragan Nikolic,
  Vaibhav Palkar,
  Spencer Patty,
  Jonathan Perry-Houts,
  Giuseppe Pitton,
  Ce Qin,
  Jonathan Robey,
  Mayank Sabharwal,
  Ali Samii,
  Alberto Sartori,
  Daniel Shapero,
  Martin Steigemann,
  Jihuan Tian,
  Jaeryun Yim,
  Liang Zhao

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[4]{Rene Gassm\"{o}ller}
\affil[4]{Department of Earth and Planetary Sciences,
  University of California Davis,
  One Shields Avenue,
  CA-95616 Davis, USA.
  {\texttt{rgassmoeller@ucdavis.edu}}}

\author[5]{Timo Heister}
\affil[5]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[6]{Luca Heltai}
\affil[6]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

\author[7]{Martin Kronbichler}
\affil[7]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[8]{Matthias Maier}
\affil[8]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

\author[9]{Jean-Paul Pelteret}
\affil[9]{Chair of Applied Mechanics,
  University of Erlangen-Nuremberg,
  Egerlandstr.\ 5,
  91058 Erlangen,
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

 \author[10]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[10]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}

\author[11]{David Wells}
\affil[11]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA.
  {\texttt{wellsd2@rpi.edu}}}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
\marginpar{update}
  Rajat Arora,
  Mauro Bardelloni,
  Conrad Clevenger,
  Sam Cox,
  Toby D. Young,
  Juliane Dannberg,
  Nicola Demo,
  Patrick Esser,
  Niklas Fehn,
  Joscha Gedicke,
  Nicola Giuliani,
  Sebastian Gonzalez-Pintor,
  Ryan Grove,
  Michael Harmon,
  Daniel Jodlbauer,
  Guido Kanschat,
  Justin Kauffman,
  Eldar Khattatov ,
  Uwe Koecher,
  Alex Kokomov,
  Paul Kuberry,
  Dustin Kumor,
  Konstantin Ladutenko,
  Karl Ljungkvist,
  Andrew McBride,
  Mathias Mentler,
  Andrea Mola,
  Dragan Nikolic,
  Vaibhav Palkar,
  Spencer Patty,
  Jonathan Perry-Houts,
  Giuseppe Pitton,
  Ce Qin,
  Jonathan Robey,
  Mayank Sabharwal,
  Ali Samii,
  Alberto Sartori,
  Daniel Shapero,
  Martin Steigemann,
  Jihuan Tian,
  Jaeryun Yim,
  Liang Zhao
